---
title: "Mood, Sleep, and Activities Pre vs Post COVID"
author: "Sarah Parker, Megan McMahon"
date: "10/23/2020"
output: 
  html_document:
    df_print: kable

---

If you don't already have the pacakges below installed, you can install them using `install.packages(packagename)` in the console.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readr)
library(tidyverse)
library(dplyr)
library(reshape2)
library(knitr)

# add more libraries here as needed
```

## Load Data

```{r cars, echo = FALSE, message = FALSE}

# change the file path to wherever the data file is on your computer
d <- read_csv("~/Box/CogNeuroLab/Wearables/data/sleep_diaries/qualtrics_sleep_survey.csv")

```

To simplify things, we are going to subset the qualtrics dataset to only contain the date, subject ID, and survey responses. 

```{r}

d <- d %>%
  select(Subject, StartDate, matches("Q."))

head(d)

```

We are also going to create a variable called questions that has what each "Q_" represents in the dataset.

```{r}

questions <- d[1, ]
questions

d <- d[-(1:2),]
```

We can search what question means what using this:
```{r}

questions[1, grep("sleep", questions[1,])] # change sleep for other keywords
```


Now we need to create a new variable called age_group. In this dataset, participants with subject IDs that begin with 1 are young adults, and those with subject IDs that begin with 2 are older adults.

```{r}
d$age_group <- ifelse(d$Subject <= 20000, "Young Adult", "Older Adult")

d %>%
  select(Subject, age_group)

```


```{r}
## find mean of sleep quality, mood, other measures, grouped by subject
## google aggregate means by subject
d_means <- d %>%
  group_by(Subject) %>%
  summarize(stressed_mean = mean(as.numeric(Q26_1), na.rm = T), 
            ruminate_mean = mean(as.numeric(Q27_1), na.rm = T), 
            sad_mean = mean(as.numeric(Q24_5), na.rm = T), 
            happy_mean = mean(as.numeric(Q25_1), na.rm = T))

d_means$Group <- ifelse(d_means$Subject <= 20000, "Young Adult", "Older Adult")

# get mean
head(d_means)

```

Now we can make plots!

```{r}
### age group differences (boxplots, violin plots)

d_means %>%
  select(-Subject) %>%
  melt(id.vars = "Group") %>%
  ggplot(aes(value, group = Group, fill = Group, alpha = 0.75)) +
    facet_wrap(~ variable, scales = "free", ncol = 2) +
    geom_density() + 
  theme_classic() + scale_fill_brewer(palette = "Set1") +
  ggtitle("Mood by Age Group") + xlab("") + theme(axis.text.x = element_blank())

```

### To Do
* How to also look at sleep variables with respect to these mood measures? May need to recode the sleep variables
* Exploratory scatter plots (below)
* Merge with redcap survey data later on

```{r}
### scatterplots (sleep vs. mood, activities vs. mood)
## exploratory analysis on new_df- *google*, remove subject numbers, dates
```

